Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2017-04-17 teaching.tex
revise for 3-player game with S preferring SQ

\vskip1in
\section{Players and Strategy Spaces}
\begin{enumerate}
	\item Home government (G) chooses $S_G \in \left\{SQ,C\right\}$ where SQ means 'Status Quo' of unrecognized statehood and C means 'Cede' the issue of status and recognize the secessionists as an independent state.
	\item Secessionists (S) choose $S_S \in \left\{SQ,C\right\}$, same as for $G$ except when they Cede, they rejoin the home state.
	\item Patron state (P) chooses $p \in [0,\infty)$ to invest in the secessionists status quo payoffs
	\item International community (C) chooses $c \in [0,\infty)$ to invest in the secessionists payoffs from rejoining the home state
\end{enumerate}

\vskip1in
\section{Payoffs}
The payoffs after (SQ,SQ) are -p,-c,

\vskip1in
\section{Model}
N
\begin{itemize}
	\item 
\end{itemize}

>>>>

\vskip.5in
\section{Players and Strategy Spaces}
\begin{enumerate}
	\item Home government (G) chooses $S_G \in \left\{SQ,C\right\}$ where SQ means 'Status Quo' of unrecognized statehood and C means 'Cede' the issue of status and recognize the secessionists as an independent state.
	\item Secessionists (S) choose $S_S \in \left\{SQ,C\right\}$, same as for $G$ except when they Cede, they rejoin the home state.
	\item Patron state (P) chooses $p \in [0,\infty)$ to invest in the secessionists status quo payoffs
%	\item International community (C) chooses $c \in [0,\infty)$ to invest in the secessionists payoffs from rejoining the home state
\end{enumerate}

\vskip.5in
\section{Payoffs}
Let, for instance, ($SQ,C$) mean that $G$ plays $SQ$ and $S$ plays $C$. \\

Let us consider a first case where the payoffs for the secessionists are higher in the unrecognized state ('Status Quo') than they are if they cede and rejoin the home state. This, for instance, may be the case very early after taking control of the territory before their economic situation has had a chance to deteriorate.
Then 
\begin{itemize}
	\item The payoffs after ($SQ,SQ$) are $-p,3,2+p$
	\item The payoffs after ($SQ,C$) are $-10-p,5,0$
	\item The payoffs after ($C,SQ$) are $3-p,0,5+p$
	\item The payoffs after ($C,C$) are $-p,3,2$
\end{itemize}

\vskip.5in
\section{Model}
N
\begin{itemize}
	\item 
\end{itemize}
